Structured Versus Decorated Cospans

### 2021-01-11 cospans.tex
date
in Theorem 3.1: "finite colimits" |-> "finite coproducts"

% Structured versus decorated cospans
% John Baez, Kenny Courser and Christina Vasilakopoulou
% in LaTeX
% 2021/1/7

@@

\begin{proof}
This was proved in \cite[Theorems~2.3 \& 3.9]{BC}, where all the structures are specified in detail.  In fact, the double category structure only requires that $\X$ have pushouts, whereas the symmetric monoidal structure also requires that $\X$ and $\A$ have finite colimits and that $L$ preserve finite coproducts \cite[Theorem~3.2.3]{CourserThesis}.
\end{proof}

>>>>

% Structured versus decorated cospans
% John Baez, Kenny Courser and Christina Vasilakopoulou
% in LaTeX
% 2021/1/8

@@

\begin{proof}
This was proved in \cite[Theorems~2.3 \& 3.9]{BC}, where all the structures are specified in detail.  In fact, the double category structure only requires that $\X$ have pushouts, whereas the symmetric monoidal structure also requires that $\X$ and $\A$ have finite coproducts and that $L$ preserve finite coproducts \cite[Theorem~3.2.3]{CourserThesis}.
\end{proof}
